Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-10 paper.tex
addresed another reviewer comment and added a ref

The major difficulty with enumeration (apart from the size of the search space, which is thought to be in the order of
$10^{60}$ molecules for 30 heavy atoms) is that the \emph{in silico}
representation of molecules, the so-called molecular graphs, are
labeled objects (i.e. labeled graphs), while the atoms of a molecule
are of course not uniquely labeled. The mathematical concept to tackle
this problem is to consider orbits of labeled molecular graphs under
the operation of the symmetric group. However, when enumerating molecular
structures, one has thus to solve the so--called isomorphism problem, where molecules that seem different are actually
equivalent (i.e., their atoms can be mapped on top of each other by keeping the connectivity between atoms intact).
The good news is that isomorphism can be solved in polynomial time for
molecular graphs due to the fact that molecules belong to a restricted
class of graphs known as \emph{bounded valence graphs}; however, that
same restriction prevents applying to a molecular graph the polynomial
delay enumeration results obtained for general graphs (Chapter 8 in~\cite{faulon2010}). While the complexity of molecular graph
enumeration remains an open problem it has nonetheless been shown that
molecules can be sampled efficiently~\cite{goldberg1999}. Sampling
procedures based on the Metropolis or the Genetic Algorithms have been
developed and used to elucidate natural compounds from NMR data.

>>>>

The major difficulty with enumeration (apart from the size of the
search space, which is thought to be in the order of $10^{60}$
molecules for 30 heavy atoms \cite{Bohacek:1996ve}) is that the
\emph{in silico} representation of molecules, the so-called molecular
graphs, are labeled objects (i.e. labeled graphs), while the atoms of
a molecule are of course not uniquely labeled. The mathematical
concept to tackle this problem is to consider orbits of labeled
molecular graphs under the operation of the symmetric group. However,
when enumerating molecular structures, one has thus to solve the
so--called isomorphism problem, where molecules that seem different
are actually equivalent (i.e., their atoms can be mapped on top of
each other by keeping the connectivity between atoms intact).  The
good news is that isomorphism can be solved in polynomial time for
molecular graphs due to the fact that molecules belong to a restricted
class of graphs known as \emph{bounded valence graphs}; however, that
same restriction prevents applying to a molecular graph the polynomial
delay enumeration results obtained for general graphs (Chapter 8
in~\cite{faulon2010}). While the complexity of molecular graph
enumeration remains an open problem it has nonetheless been shown that
molecules can be sampled efficiently~\cite{goldberg1999}. Sampling
procedures based on the Metropolis or the Genetic Algorithms have been
developed and used to elucidate natural compounds from NMR data.
